Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes: There was difficulty as color could not provide a very accurate differentiation.

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
getwd()
setwd('C:/Users/Ashmeet/Desktop/Udacity/')
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) + 
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)

```

```{r}
library(dplyr)
pf.fc_by_age_gender <- pf %.%
  filter(!is.na(gender))%.%
  group_by(age, gender) %.%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(as.numeric(friend_count)),
            n = n()) %.%
  ungroup() %.%
  arrange(age)

head(pf.fc_by_age_gender)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(x = age, y = median_friend_count),
       data = subset(pf.fc_by_age_gender, !is.na(gender))) + 
  geom_line(aes(color = gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:   install.packages("tidyr") # only need to run this once library(tidyr) spread(subset(pf.fc_by_age_gender, select = c('gender', 'age', 'median_friend_count')), gender, median_friend_count)

***

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)

#make a new data frame, which takes all the original variables on the left of the ~ and all the new custom variables on its right. value.var takes in the variable that has to be projected on variable to the right of the ~ sign.
pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')

head(pf.fc_by_age_gender.wide)

```


***

### Ratio Plot
Notes:
# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash
#geom_hline is a kind of a reference line for the plot
```{r Ratio Plot}
ggplot(aes(x = age, y = female/male),
       data = pf.fc_by_age_gender.wide) + geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - (pf$tenure/365))
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
summary(pf$year_joined)
#gives a table summary, example:
# 2005  2006  2007  2008  2009  2010  2011  2012  2013  2014 
#    9    15   581  1507  4557  5448  9860 33366 43588    70 
table(pf$year_joined)

pf$year_joined.bucket <- cut(pf$year_joined, c(2004,2009,2011,2012,2014))
table(pf$year_joined.bucket)
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(pf$year_joined.bucket)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) + geom_line(stat = 'summary', fun.y = mean, linetype = 2)


```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf, tenure >= 1), summary(friend_count/ tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) + 
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) 

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)


ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))


```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv('yogurt.csv')
str(yo)

#to change id fro int to factor
yo$id <- factor(yo$id)
str(yo)

#histogram

```
ggplot(aes(x = price), data = yo) + geom_histogram(bin = 10)
***

### Number of Purchases
Notes:

```{r Number of Purchases}
yo <- transform(yo, all.purchases = strawberry + blueberry +
                pina.colada + plain + mixed.berry)
```

***

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(aes(x = time, y = alpha), data = yo)+
  geom_jitter(alpha = 1/20)
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids <- sample(levels(yo$id), 16)


ggplot(aes(x = time, y = price),
       data = subset(yo, id %in% sample.ids)) +
  facet_wrap( ~ id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)

#quiz
set.seed(4000)
sample.ids <- sample(levels(yo$id), 16)


ggplot(aes(x = time, y = price),
       data = subset(yo, id %in% sample.ids)) +
  facet_wrap( ~ id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:ggpirs is used to generate the scatterplot matrix.
```{r}
install.packages('GGally')
library(GGally)
theme_set(theme_minimal(20))

#set seed for reproducible results
set.seed(1836)
pf_subset <- pf[, c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset), 1000), ])

#Quiz
set.seed(1836)
pf <- pf[sample.int(nrow(pf), 1000), -1]
cor.test(pf$friendships_initiated, pf$friend_count, method = 'pearson')
cor.test(pf$mobile_likes, pf$age, method = 'pearson')
```

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

