```{r}
library(ggplot2)
data(diamonds)
```

#price of all the diamond set 
```{r}

qplot(x = price, data = diamonds)
```

#diamond count
```{r}
sum(diamonds$price < 500)
sum(diamonds$price < 250)
sum(diamonds$price >= 15000)
```


```{r}
qplot(x = price, data = diamonds, binwidth = 1)+ scale_x_continuous(limits = c(0, 1000), breaks = seq(0,1000,50))
```

# Break out the histogram of diamond prices by cut.
```{r}
qplot(x = price, data = diamonds, binwidth = 1)+facet_wrap(~cut) 
  
```


```{r}
by(diamonds$price,diamonds$cut,max)
by(diamonds$price,diamonds$cut,summary)
```

```{r}
qplot(x = price, data = diamonds, binwidth = 1) + facet_wrap(~cut , scales="free_y")

```

# Create a histogram of price per carat
# and facet it by cut. You can make adjustments
# to the code from the previous exercise to get
# started.

```{r}
qplot(x = log10(price/carat), data = diamonds, binwidth = .1)+facet_wrap(~cut)

```

# Investigate the price of diamonds using box plots,
# numerical summaries, and one of the following categorical
# variables: cut, clarity, or color.
```{r}
qplot (x = cut ,y = price, data = diamonds, geom = 'boxplot')+
  coord_cartesian(ylim = c(0, 8000))
qplot (x = clarity ,y = price, data = diamonds, geom = 'boxplot')+
  coord_cartesian(ylim = c(0, 8000))
qplot (x = color ,y = price, data = diamonds, geom = 'boxplot')+
  coord_cartesian(ylim = c(0,8000))
qplot (x = color ,y = price, data = diamonds, geom = 'boxplot')+
  scale_y_continuous(lim = c(0,8000), breaks = seq(0, 8000, 100))

by(diamonds$price, diamonds$cut, summary)
by(diamonds$price, diamonds$clarity, summary)
by(diamonds$price, diamonds$color, summary)
```


```{r}
by(diamonds$price,diamonds$color, summary)
value_1 <- IQR(subset(diamonds, color == 'D')$color)
IQR(subset(diamonds, color == 'J')$color)
```

# Investigate the price per carat of diamonds across
# the different colors of diamonds using boxplots.

```{r}
qplot (x = color ,y = price/carat, data = diamonds, geom = 'boxplot')+
  coord_cartesian(ylim = c(0, 8000))
```

#Carat using a frequency polygon
```{r}
qplot (x = carat, data = diamonds,
       binwidth = .1, geom = 'freqpoly')+ scale_x_continuous(lim = c(0,5), breaks = seq(0, 5, .1))

by(sum(diamonds),diamonds$carat, summary)

```

# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to download a data set of your choice
# and create 2-5 plots that make use of the techniques from Lesson 3.

```{r}
af <- read.csv('Agriculture.xlsx')

```
